Death by Dropdown? Engineer Insightful Shiny Apps with Behavioral Science

### 2025-09-08 conference-materials/2025_posit-conf/draft.qmd
Refactor UI and update visuals for BID redesign
- Streamlined primary filter UI into a single card with improved layout and framing toggle integration.
- Fixed issues in the satisfaction plot by explicitly adding the Target column and using dynamic color logic.
- Corrected toggle icon logic to avoid passing icon objects to `updateActionButton`.
- Updated screenshots in the presentation and Quarto documents to reflect the redesigned UI.
- Removed outdated and unused image files (`before-overload.png`, `gap-frame.png`, etc.).
- Replaced image references in HTML and QMD files to match current fil

![](img/before-overload.png)

@@

::: {.column width="50%"}
![](img/telemetry-sessions-heatmap.png)
:::
::::

@@

:::: {.columns}
::: {.column width="50%"}
### Before: Chaos
<!-- ![](img/before-overload.png) -->

@@

::: {.fragment}
![](img/summary-report.png)

>>>>

![](img/ui-before.png)

@@

::: {.column width="50%"}
![](img/telemetry-sessions.png)
:::
::::

@@

:::: {.columns}
::: {.column width="50%"}
### Before: Chaos
<!-- ![](img/ui-before.png) -->

@@

::: {.fragment}
![](img/ui-summary.png)
